### 2024-07-20 mythbusters.qmd
20240720 - player_id

# Calculate Per Game Totals
nfl_actualStatsContracts_seasonal <- nfl_actualStatsContractsSubset_offense_weekly %>% 
  dplyr::group_by(playerMerge, season) %>% 
  dplyr::summarise(
    position_group = petersenlab::Mode(position_group),
    rushing_yards = sum(rushing_yards, na.rm = TRUE), # season total
    carries = sum(carries, na.rm = TRUE), # season total
    rushing_epa = mean(rushing_epa, na.rm = TRUE),
    receiving_yards = mean(receiving_yards, na.rm = TRUE),
    receiving_epa = mean(receiving_epa, na.rm = TRUE),
    contractYear = mean(contractYear, na.rm = TRUE),
    games = n(),
    .groups = "drop_last"
  ) %>% 
  dplyr::mutate(
    ypc = rushing_yards / carries,
    contractYear = factor(
      contractYear,
      levels = c(0, 1),
      labels = c("no", "yes")
    ))

@@

@@

```{r}
mixedModel_qbr <- lmerTest::lmer(
  qbr ~ contractYear + (1 | playerMerge),
  data = nfl_contractYearQBR_seasonal
)

@@

```{r}
mixedModel_ptsAdded <- lmerTest::lmer(
  pts_added ~ contractYear + (1 | playerMerge),
  data = nfl_contractYearQBR_seasonal
)

@@

```{r}
mixedModel_epaPass <- lmerTest::lmer(
  epa_pass ~ contractYear + (1 | playerMerge),
  data = nfl_contractYearQBR_seasonal
)

@@

```{r}
mixedModel_ypc <- lmerTest::lmer(
  ypc ~ contractYear + (1 | playerMerge),
  data = nfl_actualStatsContractsRB_seasonal
)

@@

```{r}
mixedModel_epaRush <- lmerTest::lmer(
  rushing_epa ~ contractYear + (1 | playerMerge),
  data = nfl_actualStatsContractsRB_seasonal
)

@@

```{r}
mixedModel_receivingYards <- lmerTest::lmer(
  receiving_yards ~ contractYear + (1 | playerMerge),
  data = nfl_actualStatsContractsWRTE_seasonal
)

@@

```{r}
mixedModel_epaReceiving <- lmerTest::lmer(
  receiving_epa ~ contractYear + (1 | playerMerge),
  data = nfl_actualStatsContractsWRTE_seasonal
)

>>>>

# Calculate Per Game Totals
nfl_actualStatsContracts_seasonal <- nfl_actualStatsContractsSubset_offense_weekly %>% 
  dplyr::group_by(player_id, season) %>% 
  dplyr::summarise(
    player_display_name = petersenlab::Mode(player_display_name),
    position_group = petersenlab::Mode(position_group),
    rushing_yards = sum(rushing_yards, na.rm = TRUE), # season total
    carries = sum(carries, na.rm = TRUE), # season total
    rushing_epa = mean(rushing_epa, na.rm = TRUE),
    receiving_yards = mean(receiving_yards, na.rm = TRUE),
    receiving_epa = mean(receiving_epa, na.rm = TRUE),
    contractYear = mean(contractYear, na.rm = TRUE),
    games = n(),
    .groups = "drop_last"
  ) %>% 
  dplyr::mutate(
    player_id = as.factor(player_id),
    ypc = rushing_yards / carries,
    contractYear = factor(
      contractYear,
      levels = c(0, 1),
      labels = c("no", "yes")
    ))

@@

nfl_contractYearQBR_seasonal <- nfl_contractYearQBR_seasonal %>% 
  group_by(playerMerge) %>%
  mutate(player_id = as.factor(as.character(cur_group_id())))

@@

```{r}
mixedModel_qbr <- lmerTest::lmer(
  qbr ~ contractYear + (1 | player_id),
  data = nfl_contractYearQBR_seasonal
)

@@

```{r}
mixedModel_ptsAdded <- lmerTest::lmer(
  pts_added ~ contractYear + (1 | player_id),
  data = nfl_contractYearQBR_seasonal
)

@@

```{r}
mixedModel_epaPass <- lmerTest::lmer(
  epa_pass ~ contractYear + (1 | player_id),
  data = nfl_contractYearQBR_seasonal
)

@@

```{r}
mixedModel_ypc <- lmerTest::lmer(
  ypc ~ contractYear + (1 | player_id),
  data = nfl_actualStatsContractsRB_seasonal
)

@@

```{r}
mixedModel_epaRush <- lmerTest::lmer(
  rushing_epa ~ contractYear + (1 | player_id),
  data = nfl_actualStatsContractsRB_seasonal
)

@@

```{r}
mixedModel_receivingYards <- lmerTest::lmer(
  receiving_yards ~ contractYear + (1 | player_id),
  data = nfl_actualStatsContractsWRTE_seasonal
)

@@

```{r}
mixedModel_epaReceiving <- lmerTest::lmer(
  receiving_epa ~ contractYear + (1 | player_id),
  data = nfl_actualStatsContractsWRTE_seasonal
)
